How residence time constrains diversity

### 2015-06-20 paper/Manuscript.Rmd
finishing up Results -KL

>>>>

The random selection of trait values of new species (whether immigrating or evolving) allowed realistic and unreasonable trait combinations to occur. For example, a species requiring little maintenance but capable of rapid growth was possible. However, the trait combinations that persisted in the model were realistic combinations of traits that point to life history trade-offs.
